\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Administrative Manual}

\begin{document}
\tableofcontents
\appendix
\maketitle

\begin{document}
\maketitle
\section{Introduction}

Toadally Real Graphs is a multi-functional tool designed for graph visualization, bibliography searching, and graph recognition. Utilizing adjacency matrices, users can input graph data and visualize relationships between nodes. Additionally, our program includes administrative parsing capabilities for managing administrative data. Our program offers graph recognition functionality, allowing users to determine whether inputted graphs are recognizable or not.
\section{Man Pages}
\subsection{Accessing Man pages}
There are three different man pages offering information on how to navigate the admin tool (TRGadmin), how to launch the server (TRGserver), as well as how to run tests (TRGtesting). All of these man pages can me accessed from the Documentation folder (NathanInc/DOCUMENTATION) by running the following command in the command line:

man ./[man page name]

Example:
man ./TRGadmin
\subsection{TRGadmin}

TRGadmin  The admin tool is designed to allow administrators to quickly and easily make changes to the website.  The tool will automatically determine which table the data is intended for based on the syntax.

Bibliography entries must be in a file exclusively for bibs; however, you can add to multiple tables using a single file  (again excluding the bibliography table) as long as the sytnax for that entry matches the spefified table.

For the bibliography entries must be added in the file as bibtex citations where each element is separated by a new line.  This table can not contain additional "{}" besides the opening and closing ones!  There must also be exactly one blank line between each citation in the file. For the other three tables, each new entry must be on a single line. Again, that entry's syntax must match the specified table.

When removing rows, any combination of tables can be modified from a single file.  Each row to be removed must be on a single line, and all tables use the same synatax.

When updating cells, any combination of tables can be modified from a single file.  Each cell change must be on a single line, and all tables use the same syntax.


       Add file syntax for each table:
     \begin{verbatim}
       CHECK1$BIBKEY$FORMULA  CHECK2$BIBKEY$FORMULA$FUNCTION SANITIZE$FORMULA

  (bibtex example)
    @article{BIBKEY,
      author= "author",
      title= "title",
      year="year"
    }
   \end{verbatim}

\begin{verbatim}
2. Remove files syntax for each table: TABLE$BIBKEY
3. Update files syntax for each table: TABLE$NEW_VALUE$COLUMN$BIBKEY
4. For updating from table: SANTIZEN$NEW$COLUMN$OLD
\end{verbatim}

\begin{verbatim}
TABLE$NEW_VALUE$COLUMN$BIBKEY
\end{verbatim}
OPTIONS
       -a, --add
              Add information to the database.

       -d, --delete
              Delete a row from the specified table.

       -f, --file
              Specify a file to import data from.

       -h, --help
              Displays help menu.

       -p, --print
              Print elements from the specified table.

       -t, --table
              Select a specific table in the database

       -u, --update
              Update a cell in the database.
\subsection{TRGserver}
TRGserver For the formulas in our database, we defined our own syntax for adding condition statements.  Formulas can only contain one conditional per formula, so boolean logic must used if more are  needed.   Eval() evaluates python syntax, so in most cases all other syntax in the formulas can be used as such.  However, We had to require certain python3 key words to be substituted to avoid  conflicts  with  variable  names. The statements before and after the colon must have a statement even if it is just True. The constructors used to draw the graphs are stored in builder.py. To add a constructor for a theorem, simply add a function that returns an adjacency matrix to the builder.py file and update the CHECKTWO table entry to reflect that function name.

To Run:
./TRGserver.py

\subsection{TRGtesting}

 TRGtesting  This file provides test cases for the Api an database functions and the UI.  3 We used Silenium for the UI and pytest for everything else.

There are various ways to run the test cases.

For frontend testing:
-make ui

For backend testing:
-make test

For testing both simultaneously:
-make

\begin{table}
\centering
\begin{tabular}{l|r}
RULE & SUBSTITUTIONS \\\hline
Not & ! \\
And & \& \\
If Complete & C  \\
If Regular & R \\
Vertex Connectivity & k \\
Edge Connectivity & l \\
Minimum Degree & d \\
Maximum Degree & D \\
\end{tabular}
\caption{\label{tab:widgets}Substitutions}
\end{table}

\subsection{Dependencies}

Updated versions of the following libraries and applications are necessary to properly use all Toadally Real Graphs administrative tools.\dots


\begin{itemize}
\item Argparse
\item Base64
\item Flask
\item Jinja
\item Math
\item NetworkX
\item Os
\item PyGraphviz
\item Pytest
\item Python3
\item Random
\item Sys
\item Uuid
\end{itemize}

\bibliographystyle{alpha}
\subsection{References}
https://www.overleaf.com

\end{document}
